### 2016-07-11 overlay_fs.tex
Overlay FS done. Customized image in memory card works!

If the steps are successfully executed up to this point, the customized image
is ready to be deployed into the \ac{Raspi}s. In the following section, we
indicate how to proceed with the writing of the image into various memory
cards, although a more complex setup with a \ac{HTTP} server is also presented
in Section~\ref{sec:http} of the Appendix.

\subsection{Customized Image Writing to Memory Cards}
For a basic system setup, the final step is to write the customized image
to all the memory cards before they can be used in the \ac{Raspi}s. For
our current considered system, we do this manually for each card.
The testbed administrator needs to insert each memory card in its \ac{PC}
and follow the procedure in this section. A given card will be available as
\texttt{/dev/mmcblkX} for memory card readers or \texttt{/dev/sdX} USB-through
readers , where \texttt{X} a natural number. It is \textit{very important}
to write to the correct device as everything will be overwritten. To avoid
removing information from the wrong device, a testbed administrator can
insert / eject a memory card a couple of times and using the
\texttt{sudo lsblk} and \texttt commands to deduce the correct device.

For our case, the device was \texttt{/dev/mmcblk0}. Once identified, to write
the image to a memory card, the following command is used:

@@

After this is made, the memory card can now be started in a \ac{Raspi}.

>>>>

If the steps are successfully executed up to this point, the customized image
is available in the \texttt{\$\{IMAGE\}.img} file and ready to be deployed
into the \ac{Raspi}s. In the following section, we indicate how to proceed
with the writing of the image into various memory cards, although a more
complex setup with a \ac{HTTP} server is also presented in
Section~\ref{sec:http} of the Appendix.

\subsection{Writing Customized Image to Memory Cards}
For a basic system setup, the final step is to write the customized image
to all the memory cards before they can be used in the \ac{Raspi}s. For
our current considered system, we do this manually for each card.
The testbed administrator needs to insert each memory card in its \ac{PC}
and follow the procedure in this section. A given card will be available as
\texttt{/dev/mmcblkX} for memory card readers or as \texttt{/dev/sdbX}
USB-through readers, where \texttt{X} a natural number.

It is \textit{very
important} to write to the correct device as everything will be overwritten.
To avoid removing information from the wrong device, a testbed administrator
can insert / eject a memory card a couple of times and using the
\texttt{sudo lsblk} and \texttt commands to deduce the correct device.
For our case, the device was \texttt{/dev/sdb} in an Ubuntu distribution and
\texttt{/dev/mmcblk0} in an Archlinux distribution. Once identified, to write
the image to a memory card, the following command is used:

@@

The previous \texttt{dd} and \texttt{sync} commands for copying the image to
the SD memory card and flushing the remainder in memory to the filesystem
will take around 15 minutes to be finished. This is an average on a two-core
1.5 GHz laptop. However, other times might occur depending on the total image
size, the writing block size and the core capabilities of the testbed
administrator \ac{PC}. After this is made, it is only required
to eject the memory card and now it can be started in a \ac{Raspi}.
